Cosmological constraints from the redshift dependence of the Alcock-Paczynski effect: significant improvement in the dark energy figure of merit

### 2017-09-27 Draft/Draft1.0.tex
minor changes

\begin{abstract}
We use the small scale anisotropic clustering signal of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
12, spanning the redshift range $0.15<z<0.69$ to place constraints on the expansion history of the Universe. 
Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$,
while improving upon earlier works \citep{Li2016}, 
we present a novel use of the Alcock-Paczynski (AP) test via clustering difference between redshift bins on scales of 6-40 $h^{-1}\rm Mpc$.
This differential measure is shown to be a robust statistical tool that mitigates many systematic effects, 
allowing for competitive and unbiased constrains to be placed on cosmological parameters.
We find that our results, in combination with the CMB, BAO, SNIa and $H_0$ from Cepheid data, yield
$\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ w_a = -0.07 \pm 0.29$ (68.3\% CL). 
Adding our new AP measurements to the aforementioned results 
reduces the error bars by $\sim$30-40\%,
%and reduces the area of $w_0-w_a$ contour by 50\%.
and improves the dark energy figure of merit by a factor of 2. 
The AP method can %be combined with the standard BAO method,
greatly increase the power of ongoing and future galaxy surveys in probing dark energy.
\end{abstract}

@@

In recent years the Alcock-Paczynski (AP) test \citep{AP1979} applied to galaxy redshift samples \citep{Outram2004,Blake2011,Alam2016}, 
has allowed tight constraints to be placed on the background averaged distance scales, $D_A(z)$ and $H^{-1}(z)$.  
Assuming an incorrect cosmological model for the coordinate transformation between redshift space and comoving space
produces residual geometric distortions in the resultant galaxy distribution (see  Fig.\ref{fig_xy}). 
These distortions are induced by the fact that measured distances along 
and perpendicular to the line of sight are fundamentally different. 
Measuring the ratio of galaxy clustering in the radial and transverse directions provides a probe of this AP effect.

@@

\begin{figure*}
   \centering{
   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
   \includegraphics[height=6.5cm]{fig_nbar.eps}
   \includegraphics[width=9.0cm,]{fig_2pcf.eps}
   }
   \caption{\label{fig_TpCF}
   Splitting the SDSS galaxies into six redshift bins, and measuring the correlation function.
   Left panel: We split the BOSS DR12 galaxies into six redshift bins to measure the evolution of shape distortion.
   The blue and green solid histograms show the redshift density distribution of LOWZ and CMASS galaxies in the $\Omega_m=0.31$ $\Lambda$CDM. 
   The vertical dashed lines define the six redshift bins that are used to cut the samples.
   The number of LOWZ/CMASS galaxies in the three low/high redshift bins are listed.
   Right panel: 2D contour map of measured $\xi$ as a function of $\mu$ and $s$, from the six redshift bins of LOWZ and CMASS samples, 
      in the cosmology of $\Omega_m=0.31$ $\Lambda$CDM model.
    The black dashed lines mark the clustering region 6-40\ Mpc/h studied in the AP method.
    The six contour maps have rather similar appearance, implying small redshift evolution of $\xi$ from RSD.
   }
\end{figure*}

@@

\begin{figure*}
   \centering{
   \includegraphics[width=14cm,natwidth=6,natheight=5]{fig_con_tests.pdf}
   %\includegraphics[width=9cm,natwidth=4,natheight=4]{fig2b.pdf}
   %\includegraphics[height=8cm]{fig2b.pdf}
%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}
   }
   \caption{\label{fig_contest}
   Robustness test of the results.
   For the ``default'' constraints (pink contours) are derived using six redshift bins, 
   $\mu_{\rm max}=0.97$, $n_{\mu}=15-20$, $s=6-40 \rm Mpc/h$,
   a fiducial cosmology $\Omega_m=0.26,\ w=-1.0$ for the measurement of 2pCF,
   systematic effects estimated from Horizon Run 4 simulations, 
   and covariance estimated using 2,000 MultiDark PATCHY mocks.
   When altering these options, the results remain robust (black contours).
   }
\end{figure*}

@@

In detail, the number of pairs are only counted in a fiducial cosmology
-- which is taken as the $\Omega_m=0.26$ $\Lambda$CDM --
and ``translated'' to the measurements in a ``target'' cosmology using the relations, 
\begin{eqnarray}
 s_{\rm target} = s_{\rm fiducial} \sqrt{\alpha_{\parallel}^2 \mu_{\rm fiducial}+\alpha_{\bot}^2(1-\mu_{\rm fiducial}^2)}, \\
 \mu_{\rm target} = \mu_{\rm fiducial} \frac{\alpha_\parallel}
 {\sqrt{\alpha_{\parallel}^2 \mu_{\rm fiducial} +\alpha_{\bot}^2(1-\mu_{\rm fiducial}^2)}}
\end{eqnarray}
where $\alpha_{\bot}\equiv D_{A,\rm target}/D_{A,\rm fiducial}$,
$\alpha_{\parallel}\equiv H_{\rm fiducial}/H_{\rm target}$.
and values of $D_A$ and $H$ are computed in the effective redshifts of the six redshift bins.
In the fiducial cosmology
we measure $\xi(s,\mu)$ in an ultra high resolution of
$\Delta s = 0.2 {\rm Mpc/h}$, $\Delta \mu = 1/600$,
%Let us call this ``approximate 2pCF'' method.
%to obtain the accurate number counts 
and these small ``pixels'' are grouped to infer 
the number counts in other cosmologies, 
in large pixels of $\Delta s = 1 {\rm Mpc/h}$, $\Delta \mu = 1/120$.
%in the fiducial cosmology and group the bins in the target cosmology.
In the case when one small pixel belongs to more than one larger pixel,
a correction is applied by computing the fraction of the overlapping area.

@@

The Planck team has released the {\texttt {COSMOMC}} \citep{LB2002} outputs of four MCMC ``chains'' in the CPL model, 
using a combination of four datasets:
the full-mission Planck observations of CMB temperature and polarization anisotropies \cite{Planck2015},
the BAO distance priors measured from SDSS DR11 \citep{Anderson2013}, 6dFGS \citep{6dFGS} and SDSS MGS \citep{MGS},
the ``JLA'' SNIa sample \citep{JLA},
and the Hubble Space Telescope measurement of $H_0=70.6\pm3.3$ km/s/Mpc \cite{Riess2011,E14H0}.
These MCMC chains contain the CMB+BAO+SNIa+$H_0$ likelihood computed for $\sim$37,000 sets of cosmological parameters,
yielding constraints of %$ \Omega_m = 0.309 \pm 0.010, w_0 = -0.938 \pm 0.109, w_a = -0.38 \pm 0.41$.
%\begin{eqnarray}
% \Omega_m &=& 0.309 \pm 0.010,  \\ \nonumber
% w_0 &=& -0.938 \pm 0.109,  \\ \nonumber
% w_a &=& -0.38 \pm 0.41.
%\end{eqnarray}
\small
\begin{equation}
 \Omega_m = 0.309 \pm 0.010,\
 w_0 = -0.938 \pm 0.109,\
 w_a = -0.38 \pm 0.41.
\end{equation}
\normalsize
%To derive the constraints combined with our AP method,
%we then compute the likelihood of the SDSS LOWZ+CMASS AP measurements for each of the parameter combinations provided in the Planck chain. 
%To do this, we splited the 1,133,326 galaxies from the SDSS DR12 into six redshift bins,
%measured the 2pCF (on scales of 6-40 $h^{-1}$Mpc) in these redshift bins (see Fig.\ref{fig_nbar}).
%This enables us investigating the redshift evolution of anisotropic clustering.
%We subtracted the systematic effects based on estimations from mocks made from Horizon Run 4 simulations \citep{HR4},
%and used a $\chi^2$ function to assess the redshift dependence.
%(see Methods for further explanations).
After adding the log-likelihoods of the Planck team sample with ours, 
while also multiply the sample weights by our likelihoods, 
we derive the CMB+BAO+SNIa+$H_0$+AP constraints on CPL parameters, %$\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29$.
%\begin{eqnarray}
%\Omega_m &=& 0.301 \pm 0.008, \\ \nonumber
%w_0 &=& -1.042 \pm 0.067, \\ \nonumber
%w_a &=& -0.07 \pm 0.29.
%\end{eqnarray}
\small
\begin{equation}
 \Omega_m = 0.301 \pm 0.008,\
 w_0 = -1.042 \pm 0.067,\
 w_a = -0.07 \pm 0.29.
\end{equation}
\normalsize
While the central values of parameters do not shift appreciably,
the error bars of $w_0$ and $w_a$ are reduced by 38.4\% and 29.7\%, respectively.% $$-40\%$ by adding our method into the analysis.

@@

The derived cosmological constraints are fully consistent with a cosmological constant dark energy component having no evolution.
Adding the new AP method to the CMB+BAO+SNIa+$H_0$ constraints reduces the statistical errors on many parameters by $\sim$30-40\% 
and reduces the $w_0-w_a$ (95.4\% CL) contour by 50\%.
This constitutes a significant increase in the figure of merit constraints on $(w_0, w_a)$. 
This doubling of the figure of merit comes at no additional cost or alteration to survey design, 
thus greatly improving the overall cost-benefit consideration of large cosmological redshift surveys.

We performed a thorough test of all the possible variables in our methodology.
Fig.\ref{fig_contest} shows that 
the result is unaffected by the line-of-sight $\mu$-cut, 
the number of angular bins, 
the range of radial integration and the choice of fiducial cosmology. 
%we adopt $\mu_{\rm max}=0.99\ (0.85)$ to include more (less) regions near the LOS,
%decrease the number of angular bins to $n_{\mu}=15-20$,
%change the range of clustering to $8-30 \rm Mpc/h$,
%change the fiducial cosmology to $\Omega_m=0.26,\ w=-0.6$,
%exclude 1 or 2 high redshift bins,
%or reduce the number of mocks to 1000.
The result does not change significantly if we remove the highest redshift bin,
where the estimated systematics is comparably large.
The most striking point to note in our testing is that the 
shift in contour position is very small even when we do not include the systematic correction.
This is reassuring, since we may have worried that {\it cosmological dependence} 
of the systematic correction could influence the final result.

@@

We previously proposed to constrain cosmological parameters via 
the redshift dependence of anisotropic galaxy clustering\cite{Li2016}.
This approach enables a robust AP test on relatively small scales.
In this paper we improved the methodology and obtained tight constraints on the CPL parametrization of dark energy.
%using 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
%12 spanning the redshift range $0.15<z<0.69$ . 
%Adding our constraints to the CMB+SNIa+BAO+$H_0$ combination, the $w_0-w_a$ contour was reduced by $\sim50$\%.

The AP method presented in this work has many advantages over the `traditional' galaxy clustering method.
Since it works with the redshift evolution of the anisotropic clustering signal it significantly reduces the effect of systematics. 
It avoids the great difficulty in accurate modeling of the RSD, non-linear clustering and galaxy bias.
It is applicable on much smaller clustering scales, allowing for the inclusion of more $k$-modes and hence more information.

We believe that the presented method of clustering shells will be applied to many spectroscopic galaxy surveys. 
The current figure of merit constraints on $(w_0, w_a)$ is increased by a factor of 2 
when considering the small scale clustering shells information in combination with existing constraints. 
The analysis we perform requires no change to the typical survey strategy of large cosmological redshift surveys, 
thus we can increasing (by roughly twice) the power of ongoing and future surveys, with little to no additional cost.
We expect this approach will play an important role in helping us unveiling the mystery of dark energy.

@@

\begin{acknowledgments}
We thank the Korea Institute for Advanced Study for providing computing resources (KIAS Center for Advanced Computation Linux Cluster System).
CGS acknowledges support from the National Research Foundation (NRF,  \#2017R1D1A1B03034900). 
We thank Stephen Appleby, Seokcheon Lee, Maurice van Putten, Graziano Rossi and Yi Wang for helpful discussions.

>>>>

\begin{abstract}
We use the anisotropic clustering signal of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
12, spanning the redshift range $0.15<z<0.69$ to place constraints on the expansion history of the Universe. 
Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$,
while improving upon earlier works \citep{Li2016}, 
we present a novel use of the Alcock-Paczynski (AP) test via clustering difference between redshift bins on scales of 6-40 $h^{-1}\rm Mpc$.
This differential measure is shown to be a robust statistical tool that mitigates many systematic effects, 
allowing for competitive and unbiased constrains to be placed on cosmological parameters.
We find that our results, in combination with the CMB, BAO, SNIa and $H_0$ from Cepheid data, yield
$\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ w_a = -0.07 \pm 0.29$ (68.3\% CL). 
Adding our new AP measurements to the aforementioned results 
reduces the error bars by $\sim$30-40\%,
%and reduces the area of $w_0-w_a$ contour by 50\%.
and improves the dark energy figure of merit by a factor of 2. 
The AP method can %be combined with the standard BAO method,
greatly increase the power of ongoing and future galaxy surveys in probing dark energy.
\end{abstract}

@@

In recent years the Alcock-Paczynski (AP) test \citep{AP1979} applied to galaxy redshift samples \citep{Outram2004,Blake2011,Alam2016}, 
has allowed tight constraints to be placed on the background averaged distance scales, $D_A(z)$ and $H^{-1}(z)$.  
Assuming an incorrect cosmological model for the coordinate transformation between redshift space and comoving space
produces residual geometric distortions in the resultant galaxy distribution (see  Fig.\ref{fig_xy}). 
These distortions are induced by the fact that measured distances along 
and perpendicular to the line of sight are connected with cosmological parameters differently. 
Measuring the ratio of galaxy clustering in the radial and transverse directions provides a probe of this AP effect.

@@

\begin{figure*}
   \centering{
   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
   \includegraphics[height=6.5cm]{fig_nbar.eps}
   \includegraphics[width=9.0cm,]{fig_2pcf.eps}
   }
   \caption{\label{fig_TpCF}
   Splitting the SDSS galaxies into six redshift bins, and measuring the correlation function
   (similar figures already presented in \cite{Li2016}).
   Left panel: We split the BOSS DR12 galaxies into six redshift bins to measure the evolution of shape distortion.
   The blue and green solid histograms show the redshift density distribution of LOWZ and CMASS galaxies in the $\Omega_m=0.31$ $\Lambda$CDM. 
   The vertical dashed lines define the six redshift bins that are used to cut the samples.
   The number of LOWZ/CMASS galaxies in the three low/high redshift bins are listed.
   Right panel: 2D contour map of measured $\xi$ as a function of $\mu$ and $s$, from the six redshift bins of LOWZ and CMASS samples, 
      in the cosmology of $\Omega_m=0.31$ $\Lambda$CDM model.
    The black dashed lines mark the clustering region 6-40\ Mpc/h studied in the AP method.
    The six contour maps have rather similar appearance, implying small redshift evolution of $\xi$ from RSD.
   }
\end{figure*}

@@

\begin{figure*}
   \centering{
   \includegraphics[width=14cm,natwidth=6,natheight=5]{fig_con_tests.pdf}
   %\includegraphics[width=9cm,natwidth=4,natheight=4]{fig2b.pdf}
   %\includegraphics[height=8cm]{fig2b.pdf}
%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}
   }
   \caption{\label{fig_contest}
   Robustness test of the results.
   For the ``default'' constraints (pink contours) are derived using six redshift bins, 
   $\mu_{\rm max}=0.97$, $n_{\mu}=15-20$, $s=6-40 \rm Mpc/h$,
   a fiducial cosmology $\Omega_m=0.26,\ w=-1.0$ for the measurement of 2pCF,
   systematic effects estimated from Horizon Run 4 simulations, 
   and covariance estimated using 2,000 MultiDark PATCHY mocks.
   When we alters one of these options by using $\mu_{\rm max}=0.99$, 
   $\mu_{\rm max}=0.85$, $n_{\mu}=15-20$, $s=8-30 \rm Mpc/h$, 
   a fiducial cosmology of $\Omega_m=0.26,\ w=-0.6$, 
   excluding the last redshift bin in the analysis, 
   discarding the systematics correction, 
   or reducing the number of mocks in the estimation of covariance matrix,
   the results remain robust (black contours).
   }
\end{figure*}

@@

In detail, the number of pairs are only counted in a fiducial cosmology
-- which is taken as the $\Omega_m=0.26$ $\Lambda$CDM --
and ``translated'' to the measurements in a ``target'' cosmology using the relations, 
\begin{eqnarray}
 s_{\rm target} = s_{\rm fiducial} \sqrt{\alpha_{\parallel}^2 \mu_{\rm fiducial}^2+\alpha_{\bot}^2(1-\mu_{\rm fiducial}^2)}, \\
 \mu_{\rm target} = \mu_{\rm fiducial} \frac{\alpha_\parallel}
 {\sqrt{\alpha_{\parallel}^2 \mu_{\rm fiducial}^2 +\alpha_{\bot}^2(1-\mu_{\rm fiducial}^2)}}
\end{eqnarray}
where $\alpha_{\bot}\equiv D_{A,\rm target}/D_{A,\rm fiducial}$,
$\alpha_{\parallel}\equiv H_{\rm fiducial}/H_{\rm target}$.
and values of $D_A$ and $H$ are computed in the effective redshifts of the six redshift bins.
In the fiducial cosmology
we measure $\xi(s,\mu)$ with a high resolution of
$\Delta s = 0.2 {\rm Mpc/h}$, $\Delta \mu = 1/600$,
%Let us call this ``approximate 2pCF'' method.
%to obtain the accurate number counts 
and these small ``pixels'' are grouped to infer 
the number counts in other cosmologies, 
in large pixels of $\Delta s = 1 {\rm Mpc/h}$, $\Delta \mu = 1/120$.
%in the fiducial cosmology and group the bins in the target cosmology.
In the case when one small pixel belongs to more than one larger pixel,
a correction is applied by computing the fraction of the overlapping area.

@@

The Planck team has released the {\texttt {COSMOMC}} \citep{LB2002} outputs of four MCMC ``chains'' in the CPL model, 
using a combination of four datasets:
the full-mission Planck observations of CMB temperature and polarization anisotropies \cite{Planck2015},
the BAO distance priors measured from SDSS DR11 \citep{Anderson2013}, 6dFGS \citep{6dFGS} and SDSS MGS \citep{MGS},
the ``JLA'' SNIa sample \citep{JLA},
and the Hubble Space Telescope measurement of $H_0=70.6\pm3.3$ km/s/Mpc \cite{Riess2011,E14H0}.
These MCMC chains contain the CMB+BAO+SNIa+$H_0$ likelihood computed for $\sim$37,000 sets of cosmological parameters,
yielding constraints of %$ \Omega_m = 0.309 \pm 0.010, w_0 = -0.938 \pm 0.109, w_a = -0.38 \pm 0.41$.
%\begin{eqnarray}
% \Omega_m &=& 0.309 \pm 0.010,  \\ \nonumber
% w_0 &=& -0.938 \pm 0.109,  \\ \nonumber
% w_a &=& -0.38 \pm 0.41.
%\end{eqnarray}
\small
\begin{equation}
 \Omega_m = 0.309 \pm 0.010,\
 w_0 = -0.938 \pm 0.109,\
 w_a = -0.38 \pm 0.41.
\end{equation}
\normalsize
%To derive the constraints combined with our AP method,
%we then compute the likelihood of the SDSS LOWZ+CMASS AP measurements for each of the parameter combinations provided in the Planck chain. 
%To do this, we splited the 1,133,326 galaxies from the SDSS DR12 into six redshift bins,
%measured the 2pCF (on scales of 6-40 $h^{-1}$Mpc) in these redshift bins (see Fig.\ref{fig_nbar}).
%This enables us investigating the redshift evolution of anisotropic clustering.
%We subtracted the systematic effects based on estimations from mocks made from Horizon Run 4 simulations \citep{HR4},
%and used a $\chi^2$ function to assess the redshift dependence.
%(see Methods for further explanations).
After adding the log-likelihoods of the Planck team sample with ours, 
while also multiply the sample weights by our likelihoods, 
we derive the CMB+BAO+SNIa+$H_0$+AP constraints on CPL parameters, %$\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29$.
%\begin{eqnarray}
%\Omega_m &=& 0.301 \pm 0.008, \\ \nonumber
%w_0 &=& -1.042 \pm 0.067, \\ \nonumber
%w_a &=& -0.07 \pm 0.29.
%\end{eqnarray}
\small
\begin{equation}
 \Omega_m = 0.301 \pm 0.008,\
 w_0 = -1.042 \pm 0.067,\
 w_a = -0.07 \pm 0.29.
\end{equation}
\normalsize
%While the central values of parameters do not shift appreciably,
As a result of the additional constraint from our AP analysis,
the error bars of $w_0$ and $w_a$ are reduced by 38.4\% and 29.7\%, respectively.% $$-40\%$ by adding our method into the analysis.
It can be also noted that the central value of $w_a$ moved to zero appreciably.

@@

The derived cosmological constraints are fully consistent with a cosmological constant dark energy component having no evolution.
Adding the new AP method to the CMB+BAO+SNIa+$H_0$ constraints reduces the statistical errors on many parameters by $\sim$30-40\% 
and reduces the $w_0-w_a$ (95.4\% CL) contour by 50\%.
This constitutes a significant increase in the figure of merit constraints on $(w_0, w_a)$. 
This doubling of the figure of merit comes at no additional cost or alteration to data size, 
thus greatly improving the overall cost-benefit consideration of large cosmological redshift surveys.

We performed a thorough test of all the possible variables in our methodology.
Fig.\ref{fig_contest} shows that 
the result is unaffected by the line-of-sight $\mu$-cut, 
the number of angular bins, 
the range of radial integration and the choice of fiducial cosmology. 
%we adopt $\mu_{\rm max}=0.99\ (0.85)$ to include more (less) regions near the LOS,
%decrease the number of angular bins to $n_{\mu}=15-20$,
%change the range of clustering to $8-30 \rm Mpc/h$,
%change the fiducial cosmology to $\Omega_m=0.26,\ w=-0.6$,
%exclude 1 or 2 high redshift bins,
%or reduce the number of mocks to 1000.
The result does not change significantly if we remove the highest redshift bin,
where the estimated systematics is comparably large.
The most striking point to note in our test is that the 
shift in contour position is very small even when %we do not include the systematic correction.
the systematics are not corrected.
%This is reassuring, since we may have worried that {\it cosmological dependence} 
%of the systematic correction could influence the final result. 
This indicates that, for the data analysis of current galaxy surveys,
the systematic effects in our method may not be important.
But it remains to be seen if this is true for future galaxy surveys,
or when the cosmology dependence of the systematics effects is taken into account.

@@

In recent studies we have proposed to constrain cosmological parameters 
governing the expansion history of the universe via 
the redshift dependence of anisotropic galaxy clustering\cite{Li2016}.
This approach enables a robust AP test on relatively small scales.
In this paper we improved the methodology and obtained a tight constraint 
on the CPL parametrization of dark energy.
%using 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
%12 spanning the redshift range $0.15<z<0.69$ . 
%Adding our constraints to the CMB+SNIa+BAO+$H_0$ combination, the $w_0-w_a$ contour was reduced by $\sim50$\%.

The AP method presented in this work has many advantages over the 
`traditional' methods using galaxy clustering.
Since it works with the redshift evolution of the anisotropic clustering signal it significantly reduces the effect of systematics. 
It avoids the great difficulty in accurate modeling of the RSD, non-linear clustering and galaxy bias.
%It is applicable on much smaller clustering scales, allowing for the inclusion of more $k$-modes and hence more information. 
Our method can use the galaxy clustering signal down to
much smaller scales compared to other methods,
providing much higher statistics.

Combining our method with the CMB+SNIa+BAO+$H_0$ datasets,
the dark energy figure of merit is improved by a factor of 2.
%The method can be applied to many spectroscopic galaxy surveys.
We expect the method will play an important role in deriving cosmological constraints from future spectroscopic galaxy surveys.

@@

\begin{acknowledgments}
We thank Korea Institute for Advanced Study for providing computing resources (KIAS Center for Advanced Computation Linux Cluster System).
CGS acknowledges support from the National Research Foundation (NRF,  \#2017R1D1A1B03034900). 
We thank Stephen Appleby, Seokcheon Lee, Maurice van Putten, Graziano Rossi and Yi Wang for helpful discussions.
